Univariate Analysis

### 2017-11-13 model fitting/univariate_analysis.Rmd
added code for graphic to include in article

```{r, include = FALSE}
x <- oshitar::setup()
library(survival)
library(stringr)
library(rebus)
library(dplyr)
library(stats)
library(ggplot2)
```

@@

* cross validation paths stored in splitPlan
* set seed for reproducible results

```{r, echo = FALSE}
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
str(splitPlan)
```

### Analysis on test data

```{r, data and text variables, include = FALSE}
train1 <- x[splitPlan[[1]]$train, ]

@@

#function to get summary of cox model + append pvalue of variable from loglik test to data frame
get_pvalue <- function(variable, factor = FALSE) {
  if (factor == FALSE){
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ train1[[variable]], data = train1)
  } else {
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ as.factor(train1[[variable]]), data = train1)
  }
  summary <- summary(coxmodel)
  df <- data.frame(variable = variable, pvalue = unname(summary$logtest[[3]]))
  pvalues <- rbind(pvalues, df)
  return(pvalues)
}

# Univariate analyses (select variables with p-value < 0.01)
#===================================================================
pvalues <- get_pvalue("category")
pvalues <- get_pvalue("new_category")
pvalues <- get_pvalue("n_images")

# new_n_images (recoding to group questions with >= 6 images) 
train1$new_n_images <- as.character(train1$n_images)
train1$new_n_images[train1$n_images >= 6] <- ">= 6"
pvalues <- get_pvalue("new_n_images")

pvalues <- get_pvalue("n_tags", factor = TRUE)
pvalues <- get_pvalue("new_user")
pvalues <- get_pvalue("weekday")
pvalues <- get_pvalue("hour", factor = TRUE)
pvalues <- get_pvalue("ampm")
pvalues <- get_pvalue("title_length")
pvalues <- get_pvalue("text_length")
pvalues <- get_pvalue("device_length")
pvalues <- get_pvalue("text_till_punct")
pvalues <- get_pvalue("text_contain_punct")
pvalues <- get_pvalue("title_questionmark")
pvalues <- get_pvalue("title_beginwh")

@@

pvalues <- get_pvalue("text_all_lower")
pvalues <- get_pvalue("prior_effort")
pvalues <- get_pvalue("gratitude")
pvalues <- get_pvalue("greeting")
pvalues <- get_pvalue("update")
pvalues <- get_pvalue("newline_ratio")
pvalues <- get_pvalue("avg_tag_length")
pvalues <- get_pvalue("avg_tag_score")
pvalues <- get_pvalue("num_freq_tags")
pvalues <- get_pvalue("contain_unanswered")
pvalues <- get_pvalue("contain_answered")
```

@@

#===================================================================

# title_length
spline_title <- coxph(Surv(time_until_answer, answered) ~ pspline(title_length, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("title_length_spline", fit = spline_title)

@@

# quadratic/cubic terms

@@

#===================================================================

# text_length
spline_text <- coxph(Surv(time_until_answer, answered) ~ pspline(text_length, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("text_length_spline", fit = spline_text)

@@

#===================================================================

# device_length
spline_dev <- coxph(Surv(time_until_answer, answered) ~ pspline(device_length, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("device_length_spline", fit = spline_dev)

@@

#===================================================================

# newline_ratio
fit7 <- coxph(Surv(time_until_answer, answered) ~ pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("newline_ratio_spline", fit = fit7)

@@

#===================================================================

# avg_tag_length
fit9 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("avg_tag_length_spline", fit = fit9)

@@

#===================================================================

# avg_tag_score
fit11 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_score, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("avg_tag_score_spline", fit = fit11)

@@

```{r, echo = FALSE}
options(scipen=999)
(pvalues <- pvalues %>%
  arrange(pvalue))
```

>>>>

```{r, include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
list <- oshitar::variable_setup(out)
x <- list[[1]]

library(survival); library(stringr); library(rebus)
library(dplyr); library(stats); library(ggplot2)
```

@@

```{r, echo = FALSE}
set.seed(444)
plan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
```

### Analysis on training data

```{r, include = FALSE}
train1 <- x[plan[[1]]$train, ]

@@

# function to get summary of cox model + append pvalue of variable from loglik test to df
#===================================================================
get_pvalue <- function(variable, factor = FALSE) {
  if (factor == FALSE){
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ train1[[variable]], data = train1)
  } else {
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ as.factor(train1[[variable]]), data = train1)
  }
  summary <- summary(coxmodel)
  df <- data.frame(variable = variable, 
                   pvalue = unname(summary$logtest[[3]]))
  pvalues <- rbind(pvalues, df)
  return(pvalues)
}

# Univariate analyses (select variables with p-value < 0.01)
#===================================================================
pvalues <- get_pvalue("category")
pvalues <- get_pvalue("new_category")
pvalues <- get_pvalue("n_images")
pvalues <- get_pvalue("n_tags", factor = TRUE)
pvalues <- get_pvalue("new_user")
pvalues <- get_pvalue("weekday")
pvalues <- get_pvalue("ampm")
pvalues <- get_pvalue("title_length")
pvalues <- get_pvalue("text_length")
pvalues <- get_pvalue("device_length")
pvalues <- get_pvalue("text_contain_punct")
pvalues <- get_pvalue("title_questionmark")
pvalues <- get_pvalue("title_beginwh")

@@

pvalues <- get_pvalue("text_all_lower")
pvalues <- get_pvalue("prior_effort")
pvalues <- get_pvalue("gratitude")
pvalues <- get_pvalue("greeting")
pvalues <- get_pvalue("update")
pvalues <- get_pvalue("newline_ratio")
pvalues <- get_pvalue("avg_tag_length")
pvalues <- get_pvalue("avg_tag_score")
pvalues <- get_pvalue("contain_unanswered")
pvalues <- get_pvalue("contain_answered")
```

@@

#===================================================================
# title_length
spline_title <- coxph(Surv(time_until_answer, answered) ~ pspline(title_length, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("title_length_spline", fit = spline_title)

@@

@@

#===================================================================
# text_length
spline_text <- coxph(Surv(time_until_answer, answered) ~ pspline(text_length, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("text_length_spline", fit = spline_text)

@@

#===================================================================
# device_length
spline_dev <- coxph(Surv(time_until_answer, answered) ~ pspline(device_length, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("device_length_spline", fit = spline_dev)

@@

#===================================================================
# newline_ratio
fit7 <- coxph(Surv(time_until_answer, answered) ~ pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("newline_ratio_spline", fit = fit7)

@@

#===================================================================
# avg_tag_length
fit9 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("avg_tag_length_spline", fit = fit9)

@@

#===================================================================
# avg_tag_score
fit11 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_score, df = 0, method = "AIC"), data = train1)
pvalues <- get_pvalue_new("avg_tag_score_spline", fit = fit11)

@@

```{r, echo = FALSE}
options(scipen=999)
pvalues <- pvalues %>% arrange(pvalue)
```

### Include in the article

```{r}
train1 <- x[plan[[1]]$train, ]

# function to get summary of cox model + append pvalue of variable from loglik test to df
# ---------------------------------------------------------------------------------------
get_pvalue <- function(variable, factor = FALSE) {
  if (factor == FALSE){
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ train1[[variable]], data = train1)
  } else {
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ as.factor(train1[[variable]]), data = train1)
  }
  summary <- summary(coxmodel)
  df <- data.frame(variable = variable, 
                   pvalue = unname(summary$logtest[[3]]))
  pvalues <- rbind(pvalues, df)
  return(pvalues)
}
# ---------------------------------------------------------------------------------------

pvalues <- get_pvalue("new_category")
pvalues <- get_pvalue("new_user")
pvalues <- get_pvalue("title_questionmark")
pvalues <- get_pvalue("text_contain_punct")
pvalues <- get_pvalue("weekday")
pvalues <- get_pvalue("title_length")
pvalues <- get_pvalue("text_length")
pvalues <- get_pvalue("device_length")
pvalues <- get_pvalue("text_all_lower")
pvalues <- get_pvalue("prior_effort")
pvalues <- get_pvalue("update")
pvalues <- get_pvalue("newline_ratio")
pvalues <- get_pvalue("avg_tag_length")
pvalues <- get_pvalue("avg_tag_score")
pvalues <- get_pvalue("contain_unanswered")
pvalues <- get_pvalue("contain_answered")

options(scipen=999)
pvalues <- pvalues %>% arrange(pvalue)

rms::cph(Surv(time_until_answer, answered) ~ avg_tag_score, data = x)
rms::cph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_score), data = x)
```
